Market Expectations and Mangerial Turnover

### 2024-03-02 paper.qmd
some updates on mac for data summary

```{r}
library(dplyr)
library(purrr)
spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
# Define season_to_date() function here
season_to_date <- function(season) {
  if (is.na(season) | length(gsub("/", "", season)) == 0) {
    return(NA_real_)
  }

@@

data_helper <- spells1 |>
  mutate(row_id=row_number()) |>
  filter(is.na(Finish)&contract_expiry!="-") |>
  select(contract_expiry, Finish,row_id)
data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
spells |>
  mutate(row_id=row_number()) |>
  left_join(data_helper, by="row_id") |>
  mutate(Start = as.Date(Start),
         Finish = as.Date(Finish)) |>
  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells

@@

generator = pipeline("text-generation")
# Load model directly
# from transformers import AutoTokenizer, AutoModelForCausalLM
# 
# tokenizer = AutoTokenizer.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")
# model = AutoModelForCausalLM.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")  
# Use a pipeline as a high-level helper
#from transformers import pipeline
#pipe = pipeline("text-generation", model="mistralai/Mixtral-8x7B-Instruct-v0.1")

>>>>

```{r}
library(dplyr)
library(purrr)
#spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
spells <- read.csv("raw_data/manager_spells_from_manager_urls.csv")

# Define season_to_date() function here
season_to_date <- function(season) {
  if (is.na(season) | length(gsub("/", "", season)) == 0) {
    return(NA_real_)
  }

@@

data_helper <- spells |>
  mutate(row_id=row_number()) |>
  filter(is.na(Finish)&contract_expiry!="-") |>
  select(contract_expiry, Finish,row_id)
data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
spells |>
  mutate(row_id=row_number()) |>
  left_join(data_helper |> select(-Finish), by="row_id") |>
  mutate(Start = as.Date(Start),
         Finish = as.Date(Finish)) |>
  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
spells |> distinct(name,club,Finish) |> nrow()
# find duplicates for name,club,Finish
spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
# remove duplicates
spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) -> spells
spell <- spells |> select(club,Start,Finish) |> arrange(Finish)
spell |> filter(Finish-Start>0) -> spell
```

The raw data from transfrmarkt is then cleaned and processed to create a raw dataset of manager spells. The dataset contains the following columns:

- `name`: The name of the person in charge
- `club`: The club the manager was in charge of
- `position`: The position of the person in charge
- `Start`: The start date of the spell
- `Finish`: The end date of the spell
- `days_in_charge`: The number of days the manager was in charge of the club
- `season_start`: The start of the season the spell ended

```{r}
#| label: fig-annual-spell-count
#| fig-cap: "Annual count of manager spell ending"
library(ggplot2)
library(dplyr)
# create plot of annual count of spells using a count of finishes per season assume season starts in August
spell |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
  count(season_start) |> 
  ggplot(aes(x = season_start, y = n)) +
  geom_col(width = 0.5) +
  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
  theme_minimal() -> spell_count
plotly::ggplotly(spell_count)
```

```{r}
```

```{bash}
#!/bin/bash

# Define a function to make an HTTP request to the API and parse the response
function api_call() {
  local club_name="$1"
  local year_end_of_season="$2"
  local response=$(curl -s -H "Content-Type: application/json" \
    --data '{"model": "llama2", "prompt": "Which country is the club 
${club_name} from? What is its division level based on the year 
${year_end_of_season}?"}' http://localhost:11434/api/generate)
  echo "Processing club ${club_name} (${year_end_of_season})"
  echo "${response}" >> responses.csv
}

# Read the input CSV file with clubs and end of season dates using csvparse
input_file="input.csv"
output_file="output.csv"
IFS=$'\n'
mapfile -t clubs < <(csplit ${input_file} '{printf "%s\n" %${0}}}')
unset IFS
declare -a clubs_array=(${clubs[@]})
declare -a years_array=()
for i in $(seq 0 ${#clubs_array[*]}-1); do
  IFS=',' read -r club_name year < "${input_file}" || continue
  years_array+=("${year}")
done
unset IFS

# Loop over the clubs and call the API for each one with its respective end 
of season year
for ((i = 0; i < ${#clubs_array[@]}; i++)); do
  local club_name="${clubs_array[$i]}"
  local year="${years_array[$i]}"
  api_call "${club_name}" "${year}"
done

echo "Done processing all clubs. Total responses processed: $(wc -l < 
responses.csv)"
```

@@

generator = pipeline("text-generation")
